---
title: "Replication of Study 'What makes words special? Workds as unmotivated cues (Experiment 1A)' by Edmiston & Lupyan (2015, Cognition)"
author: "Replication Author: Reeka Estacio"
date: "`r format(Sys.time(), '%B %d, %Y')`"
format:
  html:
    toc: true
    toc_depth: 3
---

<!-- Replication reports should all use this template to standardize reporting across projects.  These reports will be public supplementary materials that accompany the summary report(s) of the aggregate results. -->

## Introduction

- [GitHub Repository](https://github.com/ucsd-psych201a/edmiston2015)
- [Pre-Registration](https://github.com/ucsd-psych201a/edmiston2015/tree/main/prereg) 
- [Paradigm](https://ucsd-psych201a.github.io/edmiston2015/)

The current study is a replication of Experiment 1A of Edmiston & Lupyan (2015), which examines the differences in which verbal labels and environmental sounds activate categories in the mind. 

Previous research suggests that environmental sounds, such as a dog's bark, activate specific mental representations of a concept (Lupyan & Thompson-Schill, 2012). For instance, a loud, deep bark might evoke the image of a large dog (e.g., a Rottweiler), whereas a high-pitched bark may bring to mind a small dog (e.g., a Yorkie). In contrast, verbal labels like the word "dog" elicit broader mental representations that encompass knoweldge of multiple instances within a category. Because verbal labels do not inherently activate instance-specific qualities, they exhibit a "label advantage," enabling listeners to identify and associate verbal labels with their referents more quickly and efficiently than environmental sounds.

Experiment 1A of Edmiston and Lupyan's 2015 is a picture verification task. Participants were presented with an auditory cue (verbal label or environmental sound) followed by an image. They were then asked to respond whether the auditory cue and image matched. Analysis of reaction times (RTs) illustrates that verbal labels are more effective than environmental sounds in facilitating category activation. Moreover, when environmental sounds are paired with incongruent images (e.g., a deep bark paired with an image of a Yorkie), the activation of conceptual knowledge is impeded, as evidenced by slower reaction times.

In the current study, we aim to replicate Experiment 1A as closely as possible to determine whether these findings replicate and generalize to a new sample of participants.

## Methods

### Power Analysis

Based on guidance from instructional staff, the sample size was determined with an a-priori power analysis with the package simr, and is adequate to achieve at least 80% power for detecting the effect reported in the original study at a significance criterion of alpha = .05 (any random effects not specified in the original paper were taken from a small pilot study). 

Therefore, we plan to obtain sample of n=50 participants (around the original sample size n=43, including seven more participants to account for online uncertainty).

### Planned Sample

In the original study, the participants for Experiment 1A consisted of n=43 undergraduates. For the current study, as justified above, we aim to obtain a sample of size n=50.

Participants will be recruited and compensated through Prolific, and will be pre-screened to ensure that they are fluent English-speaking adults with no reported hearing difficulties.

### Materials

From the original study:

"The auditory cues comprised basic-level category labels and environmental sounds for six categories: bird, dog, drum, guitar, motorcycle, and phone. For each category, we obtained two distinct environmental sound cues, e.g., <classical guitar strum>, <electric guitar strum>, and two separate images for each subordinate category, e.g., two electric guitars for <electric guitar strum>, two acoustic guitars for <electric guitar strum>. To control for cue variability, we also used two versions of each spoken category label: one pronounced by a female speaker, one by a male speaker. All auditory cues were equated in duration (600 ms.) and normalized in volume. The images were color photographs (four images per category). The materials, obtained from online repositories, are available for download at http://sapir.psych.wisc.edu/stimuli/ MotivatedCuesExp1A-1B.zip." (pp. 94)

We will use the same materials for the current replication study, as all materials were provided by the original authors.  


### Procedure	

From the original study:

"On each trial participants heard a cue and saw a picture. We instructed participants to decide as quickly and accurately as possible if the picture they saw came from the same basic-level category as the word or sound they heard Participants were tested in individual rooms sitting approximately 2400 from a monitor such that images subtended 10  10°. Trials began with a 250 ms. fixation cross followed immediately by the auditory cue, delivered via headphones. The target image appeared centrally 1 s after the off- set of the auditory cue and remained visible until a response was made. Each participant completed 6 practice and 384 test trials. If the picture matched the auditory cue (50% of trials) participants were instructed to respond ‘Yes’ on a gaming controller (e.g., <cell- phone ring> or ‘‘phone’’ followed by a picture of any phone). Otherwise, they were to press ‘No’ (e.g., <cellphone ring> or ‘‘phone’’ followed by a dog). All factors (cue type, congruence) var- ied randomly within subjects. Auditory feedback (buzz or bleep) was given after each trial." (pp. 94)

We aim to follow the original procedure of Experiment 1A as precisely as possible. However, instead of presenting the trials in-person in a lab setting, the experiment will be conducted online using jsPsych hosted on Prolific. 

For this reason, the overall task will be slightly different. Participants will be asked to respond to trials using keyboard keys ("F" indicating "Yes, "J" indicating "No") in lieu of a gaming controller. Although we are unable to enforce the experimental environment, we will introduce an audio check prior to trials and encourage participants to wear headphones and situate themselves in a quiet environment to ensure that they can sufficiently hear all auditory cues. 

### Analysis Plan

From the original study:

"All participants performed very accurately on all items (M = 97%). Response times (RTs) shorter than 250 ms. or longer than 1500 ms. were removed (292 trials removed, 1.77% of total). We fit RTs for correct responses on matching trials (‘Yes’ responses) with linear mixed regression using maximum likelihood estimation (Bates, Maechler, Bolker, & Walker, 2013), including random intercepts and random slopes for within-subject factors and random intercepts for repeated items (unique trial types) following the recommendations of Barr, Levy, Scheepers, and Tily (2013). Reported below are the parameter estimates (b) and confidence intervals for each contrast of interest. Significance tests were calculated using chi-square tests that compared nested models—models with and without the factor of interest—on improvement in log-likelihood." (pp. 94-95)

For our replication, we will follow the original analysis as closely as possible. We will exclude participants who fall below a 90% accuracy threshold, as well as trials where RTs are shorter than 250ms and longer than 1500ms. We will then replicate the linear mixed effect model to examine the same main effects and random structure. Finally, we will replicate the chi-square tests that compared the models with and without the main effect using log-likelihood.

We anticipate that the results will successfully replicate. We should find that verbal labels elicit the lowest overall reaction times, and that congruent sounds elicit lower reaction times than incongruent sounds.

[Experiment pre-registration](https://github.com/ucsd-psych201a/edmiston2015/tree/main/prereg) 

**Clarify key analysis of interest here**: Linear mixed regression model, chi-square tests of nested models with and without the factor of interest.

### Differences from Original Study

This replication will differ slightly from the original study in terms of setting and procedure. As previously mentioned, the experiments will be conducted online using jsPsych as opposed to in-person in a lab. Loading delays, internet speed, and other technical difficulties encountered on participants' personal devices may affect overall reaction times. Participants will also be using keyboard keys to respond to trials, in lieu of responding on a gaming controller. Despite these differences, we do not anticipate that these differences will significantly affect results or ability to obtain the same effect as described in the original study.

### Methods Addendum (Post Data Collection)

#### Actual Sample

  The actual sample size obtained is n=50. While the original study consisted of n=43 participants, we included seven more participants to account for online uncertainty. Participants were pre-screened to ensure that they are adult English speakers without hearing difficulties.
  
  In our replication experiment, only 84% of participants performed at an accuracy of above 90% (compared to 97% in the original study). Participants who fell below this accuracy threshold were excluded. Trials where reaction times fell below 250ms and exceeded 1500ms were also excluded. In total, 404 trials were removed from the final analysis (0.05% of total).

#### Differences from pre-data collection methods plan
  NA

## Design Review

In our analysis, one factor is directly manipulated: the auditory cue that was presented to participants. There are three conditions of that factor: verbal label, congruent sound, and incongruent sound.

There was one measure taken, which is reaction time (RT).

This study uses a within-participants design.

The measures were repeated; there were 384 experimental trials in the original experiment.

It would not make sense for the experiment to be changed to between-participants because the measures would not be as accurate. There will be individual differences of RTs regardless of experimental conditions.

No known steps were taken to reduce demand characteristics. 

They should have added attention checks between trials to ensure participants are attentive throughout trials. They could have also kept "No" responses. Incongruent sounds may have prompted participants to respond "No", but these are still valid responses.

The original study involved undergraduate participants, which raises generalizability issues because they are inherently a WEIRD population.


## Results

### Data preparation

Data preparation following the analysis plan.

The following code combines the data that has been collected from our experiment (currently Pilot B) and performs the necessary data wrangling to run through our analysis model. Similar to the original study, practice trials and "No" trials were removed. Trials where reaction times are less than 250 ms or exceed 1500 ms after stimulus presentation were also excluded. This also labels the conditions for later analysis (i.e. `congruent`, `incogruent`).
	
```{r}
### Data Preparation

#### Load Relevant Libraries and Functions
library(tidyverse)
library(readr)
library(lme4)
```

```{r}
#### Import data
## currently using pilot B data
folder_path <- "../data/pilot_b"
csv_files <- list.files(folder_path, pattern = "*.csv", full.names = TRUE)
df_list <- lapply(csv_files, read_csv)
combined_df <- bind_rows(df_list)

#### Data exclusion / filtering
#exclude 'No' trials 
combined_df <- combined_df %>%
  mutate(response = as.character(response)) %>%
  filter(response == "f")         # use "y" for pilot_a data, use "f" for pilot_b data

#exclude practice trials 
combined_df <- combined_df %>%
  filter(exp_part == "actual")

#rename "sound_subtype" to "cue"
combined_df <- combined_df %>%
  rename(cue = sound_subtype)

#create congruency column 
combined_df <- combined_df %>%
  mutate(congruency = case_when(
    cue == "label" ~ "label",
    img_subtype %in% c("song", "york", "bongo", "acoustic", "harley", "rotary") & sound_version == "A" ~ "incongruent",
    TRUE ~ "congruent"
  ))

#filter reaction time 
combined_df <- combined_df %>%
  filter(rt >250, rt <1500)

#### Prepare data for analysis - create columns etc.
combined_df <- combined_df %>%
  select(rt, ID, sound_category,cue, congruency)
```

### Confirmatory analysis

Following the confirmatory analysis of the original study, our replication will also perform a linear mixed effects regression model fit on response times to correct trials on congruent trials. The details of the analysis are specified in the "Analysis Plan" section of this writeup. Again, the current analysis is run on data collected from Pilot B.

```{r}
library(lmerTest)
library(emmeans)
library(lme4)

#shows you a comparsion between reference (congruent) and the other two values (incongruent and label)
model_full <- lmer(rt ~ congruency + (1 + congruency|ID) + (1|sound_category), data = combined_df)

summary(model_full)

#get 95% CI
confint.merMod(model_full,method="Wald")

#post-hoc test: allows you to examine relationship between incongruent and label
model_full %>% 
  emmeans(pairwise ~ congruency,
          #adjusts p values so that it is more difficult to get a significance (correction method)
          adjust = "bonferroni") %>% 
  pluck("contrasts")


#chi squared test 
model_reduced <- lmer(rt ~ (1 + congruency|ID) + (1|sound_category), data = combined_df)

anova(model_full, model_reduced)

# model for Pilot A shows us that incongruent takes longer than congruent (b = 28.7), that label is shorter than congruent (b = -15.52), and that incongruent takes longer than label (b = 44.3) 
```

*Side-by-side graph with original graph is ideal here*

### Exploratory analyses

Any follow-up analyses desired (not required).  

## Discussion

### Summary of Replication Attempt

Open the discussion section with a paragraph summarizing the primary result from the confirmatory analysis and the assessment of whether it replicated, partially replicated, or failed to replicate the original result.  

### Commentary

Add open-ended commentary (if any) reflecting (a) insights from follow-up exploratory analysis, (b) assessment of the meaning of the replication (or not) - e.g., for a failure to replicate, are the differences between original and present study ones that definitely, plausibly, or are unlikely to have been moderators of the result, and (c) discussion of any objections or challenges raised by the current and original authors about the replication attempt.  None of these need to be long.


**Jenna Brooks**: Project Administration (lea)
